quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-09 paper-quollr.Rmd
Added error lot code for Scurve

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(ggbeeswarm)
library(patchwork)
library(Rtsne)
library(uwot)
library(readr)
library(tools)
library(cardinalR)

@@

```{r, echo=TRUE}
vis_mesh(
  trimesh_data = trimesh
  )
```

@@

nldr1 <- umap_scaled1 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  theme(aspect.ratio = 1)

@@

nldr2 <- umap_scaled2 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  theme(aspect.ratio = 1)

@@

nldr3 <- umap_scaled3 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  theme(aspect.ratio = 1)

@@

nldr4 <- umap_scaled4 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  theme(aspect.ratio = 1)

@@

nldr5 <- umap_scaled5 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#636363') +
  theme(aspect.ratio = 1)

@@

nldr6 <- umap_scaled6 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  theme(aspect.ratio = 1)
```

```{r}
nldr1 + nldr2 + nldr3 + 
  nldr4 + nldr5 + nldr6 +
  plot_layout(ncol = 3)
```

>>>>

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)

@@

@@

scurve_nldr1 <- umap_scaled1 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  theme(aspect.ratio = 1) +
  interior_annotation("a", c(0.08, 0.9))

@@

scurve_nldr2 <- umap_scaled2 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  theme(aspect.ratio = 1) +
  interior_annotation("b")

@@

scurve_nldr3 <- umap_scaled3 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  theme(aspect.ratio = 1) +
  interior_annotation("c", c(0.08, 0.9))

@@

scurve_nldr4 <- umap_scaled4 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  theme(aspect.ratio = 1) +
  interior_annotation("d")

@@

scurve_nldr5 <- umap_scaled5 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#636363') +
  theme(aspect.ratio = 1) +
  interior_annotation("e")

@@

scurve_nldr6 <- umap_scaled6 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  theme(aspect.ratio = 1) +
  interior_annotation("f")
```

```{r}
scurve_error <- dplyr::bind_rows(scurve_umap_mse,
                                 scurve_umap_mse2,
                                 scurve_umap_mse3,
                                 scurve_umap_mse4,
                                 scurve_umap_mse5,
                                 scurve_umap_mse6)

scurve_error <- scurve_error |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()

error_plot <- ggplot(scurve_error,
         aes(x = a1,
             y = sqrt(MSE),
             color = method)) +
    geom_point(size = 0.8) +
    geom_line(linewidth = 0.3) +
  scale_x_continuous(breaks =
    sort(unique(scurve_error$a1))[
      seq(1, length(
        unique(scurve_error$a1)), 
        by = 5)]) +
  scale_color_manual(
    values=c('#e41a1c','#ff7f00','#4daf4a', 
             "#a65628",'#636363', '#984ea3'))+
    ylab("RMSE") +
    xlab(expression(paste("binwidth (", a[1], ")"))) +
    theme_minimal() +
    theme(panel.border = element_rect(fill = 'transparent'),
          plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
          axis.ticks.x = element_line(),
          axis.ticks.y = element_line(),
          legend.position = "none",
          axis.text.x = element_text(size = 7),
          axis.text.y = element_text(size = 7),
          axis.title.x = element_text(size = 7),
          axis.title.y = element_text(size = 7),
          aspect.ratio = 1.5)
```

```{r}
error_plot + wrap_plots(
  scurve_nldr1, scurve_nldr2, 
  scurve_nldr3, scurve_nldr4,
  scurve_nldr5, scurve_nldr6, 
  ncol = 2, widths = c(50, 50))
```

### 2025-05-09 paper-quollr.tex
Updated the image in the introduction, add section on finding the best fit
Added error lot code for Scurve

Add the image generated with S-curve data

@@

\begin{verbatim}
vis_mesh(
  trimesh_data = trimesh
  )
\end{verbatim}

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-16-1}

@@

>>>>

Add the image generated with the application

@@

@@

\subsection{Find the most appropriate fit}\label{find-the-most-appropriate-fit}

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-22-1}
